---
title: "JUPITER-06 PD-L1 TPS <1% subgroup analysis"
author: "Joseph J Zhao, MBBS^1,2^; Filippo Pietrantonio, MD^3^; Raghav Sundar, MBBS, PhD^1,2^"
date: ""
output: github_document
editor_options: 
  chunk_output_type: console
---

^1^ Yong Loo Lin School of Medicine, National University of Singapore, Singapore

^2^ Department of Haematology-Oncology, National University Cancer Institute, Singapore

^3^ Medical Oncology Department, Fondazione IRCCS Istituto Nazionale dei Tumori, Milan, Italy

### Letter in Reply to Gao *et al* - Supporting documents

Regarding concerns raised pertaining to our original article: Yap, D. W. T. *et al*. Effectiveness of Immune Checkpoint Inhibitors in Patients With Advanced Esophageal Squamous Cell Carcinoma: A Meta-analysis Including Low PD-L1 Subgroups. JAMA Oncology, doi:10.1001/jamaoncol.2022.5816 (2022). 

This Github repository contains supporting workings, data, and figures for our Letter in Reply.

### Load packages

```{r warning = FALSE, message = FALSE}
package.name=c(# data reconstruction
  "IPDfromKM",
  # data manipulation
  "tidyverse", "readr", "readxl", "dplyr", "tidyr", "lubridate", "tibble", "plyr", "devtools", "stringr", "stringi",
  # survival analysis
  "survminer", "survival", "rstpm2", "survRM2", "prodlim",
  # plotting
  "ggplot2"
)

for (package.name in package.name){
  tryCatch(
  {
  if (!require(package.name, character.only = TRUE)){ 
    install.packages(package.name, character.only = TRUE) 
    library(package.name, character.only = TRUE)} else {library(package.name, character.only = TRUE)}
  }, 
    error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}

```

### Set working directory

```{r message=FALSE, warning=FALSE}

wd="C:/Users/jzhao/OneDrive/Research_Cloud/NUH_NCIS/pdl1_escc_kms/"
setwd(wd)

```

### Load reconstructed time-to-event data of JUPITER-06 PD-L1 TPS <1% subgroups reported by Wu *et al* (figures 1B &D)

Reconstruction of survival data was conducted separately with the *IPDfromKM* package. Reconstructed data is provided in the "reconstructed_data" folder.

Reference: Wu, H. X. *et al*. Clinical Benefit of First-Line Programmed Death-1 Antibody Plus Chemotherapy in Low Programmed Cell Death Ligand 1-Expressing Esophageal Squamous Cell Carcinoma: A Post Hoc Analysis of JUPITER-06 and Meta-Analysis. J Clin Oncol, Jco2201490, doi:10.1200/jco.22.01490 (2022).

```{r warning = FALSE, message = FALSE}

files <- list.files(path = paste0(wd, "data/recon/"), pattern = paste(".csv",sep=""), full.names = T)
df <- sapply(files, read_csv, simplify=F) %>% 
          bind_rows(.id = "id") %>% 
          dplyr::select(time, status, arm, outcome)

head(df)

```

### Figure 1 Compare reconstructed KM plots to original plots

```{r fig.height=5, fig.width=5}

for (i.outcome in unique(df$outcome)){
  
  cox=coxph(Surv(time, status)~arm, data=subset(df, df$outcome==i.outcome))
  sum.cox=summary(cox)
  
  km=survfit(Surv(time, status)~arm, data=subset(df, df$outcome==i.outcome))
  
  plot_km = ggsurvplot(km,
                      data = subset(df, df$outcome==i.outcome), 
                      size=0.8,
                      risk.table = TRUE,    
                      censor.shape="|",
                      censor.size = 1.2,
                      palette = c("black","steelblue4"),
                      xlim = c(0,max(subset(df, df$outcome==i.outcome)$time)),
                      xlab = "Time, months",
                      break.time.by = 3,   
                      ggtheme = theme_bw(),
                      risk.table.y.text = F,
                      risk.table.fontsize=2.7,
                      legend.labs = (cox$xlevels$arm),
                      title=paste0("Reconstructed JUPITER-06 PD-L1 TPS<1%: ", i.outcome)
                      )
  
  print(plot_km)
}

```

### Calculate follow-up time with reverse KM method with the *prodlim* package

```{r }

quantile(prodlim(Hist(time=time, event=status)~arm, data=subset(df, df$outcome=="OS"), reverse=TRUE))

```

### Figure 2 Evaluate for proportional hazards assumption with the Grambsch-Therneau test and plotted Schoenfeld residuals

```{r warning=FALSE}

for (i.outcome in unique(df$outcome)){print(ggcoxzph(cox.zph(coxph(Surv(time, status)~arm, data=subset(df, df$outcome==i.outcome))), title=i.outcome))}

```

### Figure 3 Hazard difference over time

```{r fig.height=7, fig.width=7, message=FALSE, warning=FALSE}

for (i.outcome in unique(df$outcome)){
  
  df_temp=subset(df, df$outcome==i.outcome)
  df_temp$arm=ifelse(df_temp$arm=="Placebo plus TP", 0, 1)
  
  # fit model for stpm2 
  fit=stpm2(Surv(time, status) ~ arm, data=df_temp, df=3)
  pred=predict(fit, newdata=data.frame(arm=0), type="hdiff", var="arm", exposed=function(data) transform(data, arm=1), grid=TRUE, full=TRUE, se.fit=TRUE)
  
  plot_timevar=ggplot(pred, aes(x=time, y=Estimate, ymin=lower, ymax=upper)) +
            geom_ribbon(alpha=0.4, fill="steelblue4") + 
            geom_line(size=1, color="darkgoldenrod4") +
            theme(plot.title= element_text(face="bold", size=14), axis.text=element_text(color="black"))+
            theme_bw()+
            coord_cartesian(xlim=c(0, 0.9*max(df_temp$time)))+
            geom_hline(yintercept=0, linetype="dashed")+
            labs(color="black", x = "", y = "Hazard difference\nfavours Toripalimab plus TP | favours Placebo plus TP", 
                 title = paste0("JUPITER-06 PD-L1 TPS<1% subgroup\nHazard-difference over time from reconstructed ", i.outcome, " KM plots"), face="bold")
  
  
  # historam for censorship counts
  df_temp_censor=subset(df, df$status==0 & df$outcome==i.outcome)
    
  plot_censor=ggplot(aes(x=time, fill=arm), data=df_temp_censor)+
    geom_histogram( position="identity", width=0.2, alpha=0.3)+
    theme_bw()+
    coord_cartesian(xlim=c(0, 0.9*max(df_temp$time)))+
    labs(y="censorship count", x="Time, months")+
    scale_fill_manual(values=c("black", "steelblue4"))
  
  ggarrange(plot_timevar, plot_censor, ncol = 1, nrow = 2,
            heights = c(2, 0.5),
            common.legend = TRUE, legend = "bottom", align='v') %>% print
    
}

```    
          
Abbreviations: PD-L1, programmed death ligand 1; OS, overall survival; PFS, progression-free survival; RMST, restricted mean survival time; TPS, Tumor Proportion Score; TP, paclitaxel plus cisplatin.
